% Created 2013-11-06 Wed 10:27
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{soul}
\usepackage{textcomp}
\usepackage{marvosym}
\usepackage{wasysym}
\usepackage{latexsym}
\usepackage{amssymb}
\usepackage{hyperref}
\tolerance=1000
\providecommand{\alert}[1]{\textbf{#1}}

\title{Final Report}
\author{Matt Clifford, Jeff Drake, Jeremy High, Stephen Nusko, Matt Renaud}
\date{\today}

\begin{document}

\maketitle

\setcounter{tocdepth}{3}
\tableofcontents
\vspace*{1cm}

\section{Introduction}

\subsection{Problem Statement}

\subsection{Project Overview}

\subsection{Release Notes Summarizing the Last Transition}

\section{Software Requirements}

\section{Design Specification}

\subsection{Software Architecture (with diagrams)}

\subsection{Sequence Diagrams}

\subsection{Class Diagrams (and their relationships)}

\section{Technical Documentation}

\subsection{Programming Language and Platform}

\subsection{Algorithms, Tools, and Environment}

\subsection{Database Tables and Schema}

\section{User Documentation}

\section{Software Test Plan}
	\subsection{Overview of Testing}
		When designing the software test plan it is important to remember the environment that it will be made, and released in.
		We will start with an exploration of the purpose, expectations, and environment, before proceeding with an in-depth analysis of all the software testing processes used.
		\subsubsection{Software Purpose}
			The purpose of the software is to provide students of the local campus a common place to post and share unneeded textbooks.
			As well as provide a method for users to contact and arrange the purchase of textbooks they need for their courses. 
			The system does not control a safety-critical system; rather it brings people together for ease of use. 
			The software must be reliable in having the correct information for contacting users, and the current offerings of books.
		\subsubsection{User Expectations}
			Users expect a seamless experience of browsing for books, contacting sellers if the price point seems reasonable.
			However because it's a low key system, no personal information besides the user's name and email address and possibility phone numbers are stored.
			Users will understand if the website or server fails and must be restarted during the launch.
			However as the system becomes more popular it will be important to upgrade servers and clamp down on bugs because system failures will not be tolerated over other competitors.

		\subsubsection{Marketing environment}
			There are quite a few competing products including companies such as, Kijiji, Amazon, saveontextbooks, etc.
			However there is no website that focuses just on our personal campus so our product fills a niche that exists.
			So this product will be the true first in its own little area, but with other broader competitors.
			It therefore requires a decent level of reliability, but some down time or errors will be acceptable as long as they are not to major.

	\subsection{Development Testing}

		Our testing approach during development was based on each member was responsible for using a defect testing process to find their own errors, but as well we had some helpful tools and tests in place to help ensure defects were found. 
		We also used pair programming to have concurrent inspections ongoing.

		\subsubsection{Software Inspections}
			Jeffery Drake was in charge of inspecting and analyzing the software architecture, and database schemas. 
			Jeffery found sections of code that didn't meet our expected standard for maintainability and efficiency. 
			This caused many refactors in keeping with certain agile methods to improve the reuse of code from Django, while improving the overall architecture.  
			Matt Renaud was constantly reviewing and analyzing the requirements specification based on the current project, and on iteration meetings with our client as well as the various system prototypes. 
			Changing the specification and the working design models as needed. 
			Every member was responsible for at inspections of their own portions of code, and ensuring the entire system still worked together correctly.
		\subsubsection{Unit Testing}

			Each individual Model we created was tested using Django's automated testing suite, in the style of JUnit tests. 
			Each class and function within was tested. 
			Test cases were developed based on the real data that was taken and stored in a test database to ensure no tests could affect production data. 
			Expected output was worked out by hand, and then tested against the program output. 
			Test reports are then automatically generated by Django. 

		\subsubsection{Component Testing}

			Some of the components such as Users model, and Forms have innate testing suite, but other models like our book which includes various sub models including Author, and Subjects were tested for their integration and correct overall function. 
			Again Test cases were developed to ensure that each situation within the model was tested, multiple authors, multiple subjects, or just single, as well as verification that there can be no book without at least one of the previous parts filled out.

		\subsubsection{System Testing}

			System testing is done almost exclusively through Django's framework; there are 999 tests that test the entire subset of the program interface. 
			Every template, user, default webpage also including our unit and component tests is also included in that number. 
			This allows us to have a relatively quick method to ensure our current system build is up to specifications.

	\subsection{Release Testing}

		Unfortunately we have no separate team to look over our program, however when talking with our client it was stated that the product should be to the level of or close to finished prototype. 
		Full release testing would be done at a later date. 
		However parts can be implemented currently. 

		\subsubsection{Requirements-based Testing}

			All of our Unit and component testing contain requirement based testing. 
			Ensuring the correct output that is expected is received. 
			However other requirements such as performance and scenario require a different approach then unit and component testing can provide.

		\subsubsection{Scenario Testing}

			Must feature was tested with a use case, and some important features had a sequence diagram designed. 
			They have been attached earlier in this report. 
			Testing was done to ensure the main success story of the use case flowed correctly and achieved the desired aim.

		\subsubsection{Performance Testing}

			Again because full release testing is not possible, we have only implemented and tested some parts of the performance of the system. 
			These can be split into the following.

		\subsubsection{Failure Behaviour}

			When the service is not running on the server the response from the server renders a page explaining the page is temporarily unavailable and will be back later. 
			This will inform the customer of the issues and let the system admin have some time to find errors and correct them.

		\subsubsection{Stress Testing}

			We have been running our website throughout the various development versions uploaded and running in a production environment at Buchladen.uwinsocr.ca with no crashes so far. 
			Response time is quick and usability and reliability has been found to be excellent. 

	\subsection{User Testing}

		\subsubsection{Alpha Testing}

			Every member of the development team was responsible for defect testing, and validation testing of the current tasks they were implementing in that particular iteration. 
			Other members would also inspect the other features that were implemented to ensure no defects were missed, and to validate the correct usage, or attempt to find defects.

		\subsubsection{Beta Testing}

			Friends and the client were shown the system and encouraged to comment on anything they saw. 
			The team asked them to try and think of exceptions and invalid inputs they could use. 
			They were asked to comment on the functionality and the aesthetics, and changes were made to the project direction resulting from their recommendations.

	\subsection{Acceptance Testing}

		\subsubsection{Acceptance Criteria}

			The client agreed to requirement-based acceptance testing. 
			Many features must be in working order including; registration, login, posting books, contacting sellers, and administration abilities.

		\subsubsection{Acceptance Testing Plan}

			We will provide a suite of unit and component tests, as well system integration tools, to ensure desired functionality. 
			There will also be use case and inspections of the system's design and performance.

		\subsubsection{Acceptance Tests}
			\begin{enumerate}
				\item Unit tests
				\item Component tests
				\item System integration
				\item Inspections
				\item Scenario cases
			\end{enumerate}

		\subsubsection{Run Acceptance Tests}
			All tests have been run and passed. No major issues were found.

		\subsubsection{Reject/Accept System}
			The system has been submitted to the client for final review and acceptance.
\section{Reference}


\end{document}
